\papertitle

### 2017-01-30 paper/paper.tex
Added DAFX paper templates and Latex build stuff.

% Template LaTeX file for DAFx-17 papers
%
% To generate the correct references using BibTeX, run
%     latex, bibtex, latex, latex
% modified...
% - from DAFx-00 to DAFx-02 by Florian Keiler, 2002-07-08
% - from DAFx-02 to DAFx-03 by Gianpaolo Evangelista
% - from DAFx-05 to DAFx-06 by Vincent Verfaille, 2006-02-05
% - from DAFx-06 to DAFx-07 by Vincent Verfaille, 2007-01-05
%                          and Sylvain Marchand, 2007-01-31
% - from DAFx-07 to DAFx-08 by Henri Penttinen, 2007-12-12
%                          and Jyri Pakarinen 2008-01-28
% - from DAFx-08 to DAFx-09 by Giorgio Prandi, Fabio Antonacci 2008-10-03
% - from DAFx-09 to DAFx-10 by Hannes Pomberger 2010-02-01
% - from DAFx-10 to DAFx-12 by Jez Wells 2011
% - from DAFx-12 to DAFx-14 by Sascha Disch 2013
% - from DAFx-15 to DAFx-16 by Pavel Rajmic 2015
% - from DAFx-16 to DAFx-17 by Brian Hamilton 2016
%
% Template with hyper-references (links) active after conversion to pdf
% (with the distiller) or if compiled with pdflatex.
%
% 20060205: added package 'hypcap' to correct hyperlinks to figures and tables
%                      use of \papertitle and \paperauthorA, etc for same title in PDF and Metadata
%
% 1) Please compile using latex or pdflatex.
% 2) If using pdflatex, you need your figures in a file format other than eps! e.g. png or jpg is working
% 3) Please use "paperftitle" and "pdfauthor" definitions below

%------------------------------------------------------------------------------------------
%  !  !  !  !  !  !  !  !  !  !  !  ! user defined variables  !  !  !  !  !  !  !  !  !  !  !  !  !  !
% Please use these commands to define title and author(s) of the paper:
\def\papertitle{Templates for DAFx-17, Edinburgh, UK}
\def\paperauthorA{Author One}
\def\paperauthorB{Author Two}
\def\paperauthorC{Author Three}
\def\paperauthorD{Author Four}

@@

\ifpdf % compiling with pdflatex
  \usepackage[pdftex,
    pdftitle={\papertitle},
    pdfauthor={\paperauthorA, \paperauthorB, \paperauthorC, \paperauthorD},
    colorlinks=false, % links are activated as colror boxes instead of color text
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen; especially useful if working with a big screen :-)
  ]{hyperref}
  \pdfcompresslevel=9
  \usepackage[pdftex]{graphicx}
  \usepackage[figure,table]{hypcap}
\else % compiling with latex
  \usepackage[dvips]{epsfig,graphicx}
  \usepackage[dvips,
    colorlinks=false, % no color links
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen
  ]{hyperref}
  % hyperrefs are active in the pdf file after conversion
  \usepackage[figure,table]{hypcap}
\fi

@@

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
%\twoaffiliations{
%\paperauthorA \,\sthanks{Thanks to the predecessors for the templates}}
%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
%}
%{\paperauthorB \,\sthanks{This work was supported by the XYZ Foundation}}
%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
%}
%-------------------------------------TWO-AUTHOR HEADER ENDS------------------------------------------------------

%---------------THREE-AUTHOR HEADER STARTS (uncomment below if your paper has three authors)-----------------------
%\threeaffiliations{
%\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
%}
%{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
%}
%{\paperauthorC \,\sthanks{Illustrious contributor}}
%{\href{http://www.ntnu.edu/dafx15}{Department of Music, Norwegian} \\ University of Science and Technology \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
%}
%-------------------------------------THREE-AUTHOR HEADER ENDS------------------------------------------------------

%----------------FOUR-AUTHOR HEADER STARTS (uncomment below if your paper has four authors)-----------------------
\fouraffiliations{
\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
}
{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
}
{\paperauthorC \,\sthanks{Illustrious contributor}}
{\href{http://www.ntnu.edu/dafx15}{Department of Music,} \\ Norwegian University of Science and Technology (NTNU) \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
}
{\paperauthorD \,\sthanks{This guy is a very good fellow}}
{\href{http://dafx14.fau.de}{Fraunhofer IIS,} \\ Friedrich-Alexander University Erlangen\\ Erlangen, Germany\\
{\tt \href{mailto:dafx14@audiolabs-erlangen.de}{dafx14@audiolabs-erlangen.de}}
}
%-------------------------------------FOUR-AUTHOR HEADER ENDS------------------------------------------------------

@@

\begin{abstract}
This is the template file for the proceedings of the 20$^{\text{th}}$ International Conference on Digital Audio Effects (DAFx-17).
This template has been derived from WASPAA'99 templates and aims at producing conference proceedings in electronic form.
The format is essentially the one used for ICASSP conferences.
Please use either this \LaTeX{} or the accompanying Word formats when preparing your submission.
The templates are available in electronic form on
\href{http://dafx17.eca.ed.ac.uk/}{http://dafx17.eca.ed.ac.uk/}.
\end{abstract}

@@

\subsection{Figures}
\label{ssec:figures}
All figures should be centred on the column (or page, if the figure spans both columns).
Figure captions (in italic) should follow each figure and have the format given in Figure \ref{fft_plot}.
%
Vectorial figures are preferred. For example when using
\texttt{Matlab}, export using either Postscript or PDF format. Also,
in order to provide a better readability, figure text font size
should be at least identical to footnote font size. To do so using
\texttt{Matlab}, use the \texttt{subplot} command before plotting.
If bitmap figures are used, please make sure that the resolution is
enough for print quality. Fig. \ref{ftt_plot2} illustrates an
example of a figure spanning two columns.
%
\begin{figure}[ht]
\centerline{\includegraphics[scale=0.8]{fft_plot2}}
\caption{\label{fft_plot}{\it Sinusoid in time and frequency domain. Short captions are centred, long captions (more than 1 line) are justified.}}
\end{figure}
%
\begin{figure*}[ht]
\center
\includegraphics[width=5in]{TwoColumnSine2}
\caption{\label{ftt_plot2}{\it A figure spanning two columns, as mentioned in Sec. \ref{ssec:figures}. }}
\end{figure*}

@@

\subsection{References}
The references will be numbered in order of appearance \cite{Mitra:Kaiser:1993:DSP:handbook}, \cite{Haykin:1991:adaptive:filter}, \cite{Moorer:2000:AES:audio:millenium} and \cite{Nackaerts:2001:ICMC}. Please avoid listing references that do not appear in the text (we did the opposite in this template).

@@

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
\bibliography{DAFx17_tmpl} % requires file DAFx17_tmpl.bib

>>>>

% Template LaTeX file for DAFx-17 papers
%
% To generate the correct references using BibTeX, run
%     latex, bibtex, latex, latex
%
% 1) Please compile using latex or pdflatex.
% 2) If using pdflatex, you need your figures in a file format other than eps! e.g. png or jpg is working
% 3) Please use "paperftitle" and "pdfauthor" definitions below

%------------------------------------------------------------------------------------------
%  !  !  !  !  !  !  !  !  !  !  !  ! user defined variables  !  !  !  !  !  !  !  !  !  !  !  !  !  !
% Please use these commands to define title and author(s) of the paper:
\def\papertitle{Improved Atoms for the Distribution Derivative Method}
\def\paperauthorA{Nicholas Esterer}
\def\paperauthorB{Philippe Depalle}

@@

\ifpdf % compiling with pdflatex
  \usepackage[pdftex,
    pdftitle={\papertitle},
    pdfauthor={\paperauthorA, \paperauthorB},
    colorlinks=false, % links are activated as colror boxes instead of color text
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen; especially useful if working with a big screen :-)
  ]{hyperref}
  \pdfcompresslevel=9
  \usepackage[pdftex]{graphicx}
  \usepackage[figure,table]{hypcap}
\else % compiling with latex
  \usepackage[dvips]{epsfig,graphicx}
  \usepackage[dvips,
    colorlinks=false, % no color links
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen
  ]{hyperref}
  % hyperrefs are active in the pdf file after conversion
  \usepackage[figure,table]{hypcap}
\fi

@@

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
\twoaffiliations{
\paperauthorA \,\sthanks{}}
{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
}
{\paperauthorB \,\sthanks{}}
{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
\\ McGill University %
\\ Montreal, Quebec, Canada \\
{\tt %
\href{mailto:philippe.depalle@music.mcgill.ca}{philippe.depalle@music.mcgill.ca}}
}

@@

\begin{abstract}
TODO
\end{abstract}

@@

\subsection{Figures}
\label{ssec:figures}
All figures should be centred on the column (or page, if the figure spans both columns).
Figure captions (in italic) should follow each figure and have the format given in Figure \ref{fft_plot}.
%
Vectorial figures are preferred. For example when using
\texttt{Matlab}, export using either Postscript or PDF format. Also,
in order to provide a better readability, figure text font size
should be at least identical to footnote font size. To do so using
\texttt{Matlab}, use the \texttt{subplot} command before plotting.
If bitmap figures are used, please make sure that the resolution is
enough for print quality. Fig. \ref{ftt_plot2} illustrates an
example of a figure spanning two columns.
%
%

@@

\subsection{References}
A test reference \cite{betser2009sinusoidal}.

@@

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
\bibliography{paper} % requires file DAFx17_tmpl.bib
